\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Custom commands
\begin{document}
\include{custom-commands}

%-------------------------------------------%
%%%%%%  RESUME STARTS HERE  %%%%%

%----------HEADING----------%
\begin{center}
    \textbf{\Huge \scshape Mohamed Abuelanin} \\ \vspace{5pt}
    \seticon{faPhone} \ \small (916) 699-2205 \quad
    \href{mailto:mabuelanin@gmail.com}{\seticon{faEnvelope} \underline{mabuelanin@gmail.com}} \quad
    \href{https://www.linkedin.com/in/mabuelanin}{\seticon{faLinkedin} \underline{mabuelanin}} \quad
    \href{https://github.com/mr-eyes}{\seticon{faGithub} \underline{mr-eyes}} \quad
    \href{https://wakatime.com/@mabuelanin}{\seticon{} \underline{wakatime/mabuelanin}} \quad
\end{center}

%----------SUMMARY----------%
\section{Summary}
\textbf{Computer Scientist \& Bioinformatics Engineer} with \textbf{10\,+ years of experience in software engineering and bioinformatics applications} for microbiome and genomics research. Proven track record of designing scalable, reproducible computational frameworks that enable petabyte‑scale NGS data analysis and accelerate scientific discovery.


%-----------SKILLS-----------%
\section{Technical Skills} 
\textbf{Programming} (Python, C++, Rust) - \textbf{Web} (WebAssembly, HTML/JS/CSS, Php) - \textbf{Databases} (SQL, Neo4J/Cypher, MemGraph) - 
\textbf{Workflows} (Snakemake, NextFlow, WDL) - \textbf{DevOps} (Git, CI/CD, unit-testing, Docker, Kubernetes, AWS) - \textbf{Distributed systems} (RPC over-network programs) - \textbf{Bioinformatics} (NGS analysis, calling variants (SNPs \& INDELs), pangenomes, population-level studies, custom scalable software solutions, k-mer-based analysis).

%-----------EDUCATION-----------%
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Davis}{Davis, CA}
      {Ph.D. in Computer Science | Thesis: Petabyte-scale sequence characterization}{Sep. 2020 -- Jun. 2024}

    \resumeSubheading
      {Nile University}{Giza, Egypt}
      {M.Sc. in Communication and Information Technology | Thesis: kmer-based sequence partitioning}{Mar. 2017 -- Aug. 2020}

    \resumeSubheading
      {Higher Technological Institute}{Cairo, Egypt}
      {B.Sc. in Electrical/Biomedical Engineering | Thesis: ML-Based Taxonomic Classification}{Sep. 2011 -- Jan. 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {University of California, Davis -- Megan Dennis' Lab, Genome Center}{Davis, CA}
    {Postdoctoral Researcher – Studying genomic variation across human duplicated genes}{Jul. 2024 -- Present}
\
  \resumeSubheading
    {University of California, Davis -- Titus Brown's Lab, School of Veterinary Medicine}{Davis, CA}
    {Graduate Student Researcher – Scalable framework for massive-scale sequence QC}{Sep. 2020 -- Jun. 2024}
\
  \resumeSubheading
    {Marine Biological Laboratory (MBL)}{Woods Hole, MA}
    {Teaching Assistant, Gene Regulatory Networks Workshop}{Oct. 2023}
\
  \resumeSubheading
    {University of California, Davis}{Davis, CA}
    {Instructor, Data Analysis Collaboratory Workshop}{Jun. 2023}
\
  \resumeSubheading
    {Nile University}{Giza, Egypt}
    {Graduate Teaching Assistant, ML, Big Data, and Advanced NGS Courses}{Mar. 2019 -- Aug. 2020}
\
  \resumeSubheading
    {Artronix}{Egypt}
    {R\&D Contract Software Engineer – Programming \& Embedded Systems Instructor}{Jan. 2013 -- Nov. 2017}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------%
\section{Projects}
\noindent
\begin{tabular}{@{}p{0.25\textwidth} p{0.7\textwidth}}
  \textbf{\href{https://snipe-bio.github.io/}{snipe}} & SRA-scale lightweight sequence QC and assessment  \\
  \textbf{\href{https://snipe-bio.github.io/}{Sequencing ROI}} & Predict library complexity using alpha-diversity and rarefaction curves  \\
  \textbf{\href{https://github.com/dib-lab/kProcessor}{kProcessor}} & Efficient Sequence K-mer indexing and Analysis \\
  \textbf{\href{https://dbretina.github.io/DBRetina/}{DBRetina}} & Gene Overlap Super Network \\
  \textbf{\href{https://github.com/dib-lab/kSpider}{kSpider}} & K-mer based ultrafast pairwise DNA clustering tool \\
  \textbf{\href{https://github.com/sourmash-bio/sourmash}{sourmash}}  & Metagenome analysis and genome comparison using k-mers \\
  \textbf{\href{https://github.com/mr-eyes/denovo-rnaseq}{denovo-rnaseq}} & De novo assembly, DEGs, and annotation snakemake workflow \\
  \textbf{\href{https://github.com/mr-eyes/guidedPartitioner}{guidedPartitioner}} & RNA-Seq ref-based reads partitioning for accurate assembly \\
  \textbf{\href{https://github.com/mr-eyes/kDecontaminer}{kDecontaminer}} & RNA-Seq Decontamination tool for a cleaner de novo transcriptome assembly \\
  \textbf{\href{https://github.com/mr-eyes/codons-optimizer}{Codon Optimization Tool}} & A tool for optimizing cDNA sequences using codon usage bias for DNA vaccines \\
\end{tabular}

\end{document}
